Bayesian Clustering and Topic Discovery: \\ Adventures with Gene Expression Data

### 2017-05-11 finalreport/paper.tex
fixed figure

\subsection{Structure of Report}
We first discuss our experiments using Bayesian topic models to discover topics (i.e. related sets of genes) in scRNA-seq data: LDA in Section~\ref{ldasec}, non-parametric topic models in Section ~\ref{nonparametricsec} and Dynamic Time Models in Section~\ref{dtmsec}. Then, we discuss our experiments in clustering: Finite Mixtures in Section~\ref{mmsec}, and Integrated Topic-Clustering in Section~\ref{intsec}. We conclude our paper with our observations from across all our studies.

@@

\section{Author Contributions}
The implementation(s) and experiments involving LDA, Dirichlet Mixtures, and Dynamic Time Model was completed by SK (Section~\ref{ldasec}, Section~\ref{dtmsec}, and Section~\ref{mmsec}). KY completed the implementations and experiments involved non-parametric topic models, the clustering topic model, and the gene set enrichment test implementation (Section~\ref{nonparametricsec}, Section~\ref{intsec}, and Section~\ref{enrichment_score}). The authors contributed equally in this work.

@@

>>>>

\subsection{Structure of Report}
We first discuss our experiments using Bayesian topic models to discover topics in scRNA-seq data: LDA in Section~\ref{ldasec}, non-parametric topic models in Section ~\ref{nonparametricsec} and Dynamic Time Models in Section~\ref{dtmsec}. Then, we discuss our experiments in clustering: Finite Mixtures in Section~\ref{mmsec}, and Integrated Topic-Clustering in Section~\ref{intsec}. We conclude our paper with our observations from across all our studies.

@@

\section{Author Contributions}
The implementations and experiments involving LDA, Gaussian Mixtures, and the Dynamic Topic Model was completed by SK (Section~\ref{ldasec}, Section~\ref{dtmsec}, and Section~\ref{mmsec}). KY completed the implementations and experiments involved non-parametric topic models, the clustering topic model, and the gene set enrichment test implementation (Section~\ref{nonparametricsec}, Section~\ref{intsec}, and Section~\ref{enrichment_score}). The authors contributed equally in this work.

@@

\begin{figure*}
    \centering
    \includegraphics[width=1\textwidth]{figs/pathwaysdtm}
    \caption{Matches between the gene collections found in DTM topics and published gene sets in \texttt{MSigDB}. $k$ refers to the number of topics in the model, $t$ refers to one of three time slices.}
    \label{fig:pathwaysdtm}
\end{figure*}
